Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-05-06 manuscript_results.Rmd
update

  # Create the box plot with additional facet for categories
plt1<-  ggplot(combined_data, aes(x = week, y = value, fill = Models)) +
    geom_boxplot(color = "black") +
    scale_fill_manual(values = custom_colors) +
    facet_wrap(category ~ Models , nrow = 3) +
    labs(
      title = "A) Models without log-back transformations",
      x = "Target Week",
      y = "Mean Weighted Interval Score (WIS)"
    ) +
  scale_y_continuous(limits = c(0, 650)) +  # Set y-axis range
    theme_minimal()
plt1
ggsave(plt1, height = 8, width = 10, filename="fig1A.jpg")  
```

@@

  # Create the box plot with additional facet for categories
plt2<-  ggplot(combined_data, aes(x = week, y = value, fill = Models)) +
    geom_boxplot(color = "black") +
    scale_fill_manual(values = custom_colors) +
    facet_wrap(category ~ Models , nrow = 3) +
    labs(
      title = "B) Models with log-back transformations",
      x = "",
      y = "Weighted Interval Score (WIS)"
    ) +
  scale_y_continuous(limits = c(0, 650)) +  # Set y-axis range
    theme_minimal()
plt2
ggsave(plt2, height = 8, width = 10, filename="Fig1B.jpg")  
```

@@

ES_1WEEK <- ggplot(W1_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("1 Week Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W1_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "%",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_2WEEK <- ggplot(W2_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("2 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W2_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "%",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_3WEEK <- ggplot(W3_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("3 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W3_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "%",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

@@

```{r}
ES_4WEEK <- ggplot(W4_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("4 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W4_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "%",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

>>>>

  # Create the box plot with additional facet for categories
plt1<-  ggplot(combined_data, aes(x = week, y = value, fill = Models)) +
    geom_boxplot(color = "black") +
    scale_fill_manual(values = custom_colors) +
    facet_wrap(category ~ Models , nrow = 3) +
    labs(
      title = "A) Models without log-back transformations",
      x = "Target Week",
      y = "Mean Weighted Interval Score (WIS)"
    ) +
  scale_y_continuous(limits = c(0, 650)) +  # Set y-axis range
    theme_minimal()
plt1
#ggsave(plt1, height = 8, width = 10, filename="fig1A.jpg")  
```

@@

  # Create the box plot with additional facet for categories
plt2<-  ggplot(combined_data, aes(x = week, y = value, fill = Models)) +
    geom_boxplot(color = "black") +
    scale_fill_manual(values = custom_colors) +
    facet_wrap(category ~ Models , nrow = 3) +
    labs(
      title = "B) Models with log-back transformations",
      x = "",
      y = "Weighted Interval Score (WIS)"
    ) +
  scale_y_continuous(limits = c(0, 650)) +  # Set y-axis range
    theme_minimal()
plt2
#ggsave(plt2, height = 8, width = 10, filename="Fig1B.jpg")  
```

# Combine in a 2x2 grid
combined_plot <- (plt1 | plt2) + 
  plot_annotation(
    title = "Figure X: Mean WIS for our 24 models",
    subtitle = "Results by forecast horizon",
    theme = theme(plot.title = element_text(size = 16, face = "bold"),
                  plot.subtitle = element_text(size = 14))
  )
# Print
print(combined_plot)

# Save to file
ggsave("Fig1.jpg", combined_plot, width =13, height =7)
```

@@

ES_1WEEK <- ggplot(W1_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("1 Week Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W1_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "Percentage (%)",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_2WEEK <- ggplot(W2_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("2 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W2_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "Percentage (%)",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ES_3WEEK <- ggplot(W3_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("3 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W3_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill =  "Percentage (%)",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle

@@

```{r}
ES_4WEEK <- ggplot(W4_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("4 Weeks Ahead") +
  theme_light() +
  theme(legend.position = "right",
    plot.title = element_text(hjust = 0.5)) +
  geom_sf_text(data = W4_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE,fontface = "bold") +  # Display percentage improvement in each state
  labs(
    fill = "Percentage (%)",  # Label for the legend
       x = "",
       y = ""
  )  # Adding a subtitle
